Об оценках на диаметр плоских множеств с целочисленными расстояниями полуобщего положения \footnote{Исследование выполнено за счет гранта Российского научного фонда (проект 19-11-00197).}

### 2019-09-11 semi-general-suplinear-bound/CHEBSB_Avdeev.tex
English theorem-environments

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Автоматическая нумерация теорем (коль скоро подключен amsthm)
\theoremstyle{plain}
%\newtheorem{theorem}{Theorem}[section]
%\newtheorem{conjecture}[theorem]{Conjecture}
%\newtheorem{lemma}[theorem]{Lemma}
%\newtheorem{corollary}[theorem]{Corollary}
%\newtheorem{proposition}[theorem]{Proposition}

%\theoremstyle{definition}
%\newtheorem{definition}[theorem]{Definition}
%\newtheorem{construction}[theorem]{Construction}
%\newtheorem{remark}[theorem]{Remark}
%\newtheorem{problem}[theorem]{Problem}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{definition}
	A set $M\in\mathfrak{M}(2,n)$ is called to be in \textit{semi-general position},
	if no three points of $M$ are collinear.
	The set of all planar integral point sets in semi-general position
	is denoted by $\overline{\mathfrak{M}}(2,n)$.
\end{definition}

@@

\begin{definition}
	A set $M\in\overline{\mathfrak{M}}(2,n)$ is called to be in \textit{general position},
	if no four points of $M$ are concyclic.
	The set of all planar integral point sets in general position
	is denoted by $\dot{\mathfrak{M}}(2,n)$.
\end{definition}

@@

There are some bounds for minimal diameter of planar integral point sets in some special positions.
Assuming that the planar integral point sets contains many collinear points,
the following result holds.
\begin{theorem}~\cite[Theorem 4]{kurz2008minimum}
	For $\delta > 0$, $\varepsilon > 0$, and $P\in\mathfrak{M}(2,n)$ with
	at least $n^\delta$ collinear points, there exists a $n_0 (\varepsilon)$
	such that for all $n \geq n_0 (\varepsilon)$ we have
	\begin{equation}
		\operatorname{diam} P \geq n^{\frac{\delta}{4 \log 2(1+\varepsilon)}\log \log n}
		.
	\end{equation}
\end{theorem}
For diameter bounds for circular sets, we refer the reader to~\cite{bat2018number}.

@@

\begin{definition}
	The part of a plane between two parallel straight lines with distance $\rho$ between the lines
	is called a strip of width $\rho$.
\end{definition}

@@

\begin{corollary}
	\label{cor:solymosi_strip}
	If a triangle $T$ with integer side-lengths $a \leq b \leq c$ is situated in a strip,
	then the width of a strip is at least $\left(a - \frac{1}{4}\right)^{1/2}$.
\end{corollary}

@@

\begin{definition}
	\cite[Definition 2.5]{my-pps-linear-bound-2019}
	A \textit{cross} for points $M_1$ and $M_2$, denoted by $cr(M_1,M_2)$, is the union of two straight lines:
	the line through $M_1$ and $M_2$,
	and the perpendicular bisector of line segment $M_1 M_2$.
\end{definition}

@@

\begin{remark}
	Lemma~\ref{lem:count_of_points_on_hyperbolas} is one of the variations of~\cite{erdos1945integral}.
\end{remark}

@@

\begin{theorem}
	\label{thm:main_result}
	For every integer $n \geq 3$ we have
	\begin{equation}
		\overline{d}(2,n) \geq (n/5)^{5/4}
		.
	\end{equation}
\end{theorem}

@@

\begin{remark}
	The following result in known:
\end{remark}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Автоматическая нумерация теорем (коль скоро подключен amsthm)

% К сожалению, английского ``Definition'' в стилевом файле нет.
% Добавляю по аналогии.
\newtheorem{Definition}{\indent {\sc Definition}}
\renewcommand{\theDefinition}{\rm \arabic{Definition}}

\newtheorem{Corollary}{\indent {\sc Corollary}}
\renewcommand{\theCorollary}{\rm \arabic{Corollary}}

\newtheorem{Remark}{\indent {\sc Remark}}
\renewcommand{\theRemark}{\rm \arabic{Remark}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{Definition}
	A set $M\in\mathfrak{M}(2,n)$ is called to be in \textit{semi-general position},
	if no three points of $M$ are collinear.
	The set of all planar integral point sets in semi-general position
	is denoted by $\overline{\mathfrak{M}}(2,n)$.
\end{Definition}

@@

\begin{Definition}
	A set $M\in\overline{\mathfrak{M}}(2,n)$ is called to be in \textit{general position},
	if no four points of $M$ are concyclic.
	The set of all planar integral point sets in general position
	is denoted by $\dot{\mathfrak{M}}(2,n)$.
\end{Definition}

@@

There are some bounds for minimal diameter of planar integral point sets in some special positions.
Assuming that the planar integral point sets contains many collinear points,
the following result holds.
\begin{Theorem}~\cite[Theorem 4]{kurz2008minimum}
	For $\delta > 0$, $\varepsilon > 0$, and $P\in\mathfrak{M}(2,n)$ with
	at least $n^\delta$ collinear points, there exists a $n_0 (\varepsilon)$
	such that for all $n \geq n_0 (\varepsilon)$ we have
	\begin{equation}
		\operatorname{diam} P \geq n^{\frac{\delta}{4 \log 2(1+\varepsilon)}\log \log n}
		.
	\end{equation}
\end{Theorem}
For diameter bounds for circular sets, we refer the reader to~\cite{bat2018number}.

@@

\begin{Definition}
	The part of a plane between two parallel straight lines with distance $\rho$ between the lines
	is called a strip of width $\rho$.
\end{Definition}

@@

\begin{Corollary}
	\label{cor:solymosi_strip}
	If a triangle $T$ with integer side-lengths $a \leq b \leq c$ is situated in a strip,
	then the width of a strip is at least $\left(a - \frac{1}{4}\right)^{1/2}$.
\end{Corollary}

@@

\begin{Definition}
	\cite[Definition 2.5]{my-pps-linear-bound-2019}
	A \textit{cross} for points $M_1$ and $M_2$, denoted by $cr(M_1,M_2)$, is the union of two straight lines:
	the line through $M_1$ and $M_2$,
	and the perpendicular bisector of line segment $M_1 M_2$.
\end{Definition}

@@

\begin{Remark}
	Lemma~\ref{lem:count_of_points_on_hyperbolas} is one of the variations of~\cite{erdos1945integral}.
\end{Remark}

@@

\begin{Theorem}
	\label{thm:main_result}
	For every integer $n \geq 3$ we have
	\begin{equation}
		\overline{d}(2,n) \geq (n/5)^{5/4}
		.
	\end{equation}
\end{Theorem}

@@

\begin{Remark}
	The following result in known:
\end{Remark}
